\documentclass[12pt,addpoints]{exam}
%\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=20mm,
	top=20mm,
}
\date{October, 2023}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{Homework 1}{}{Page \thepage\ of \numpages}
\runningheadrule
\firstpagefooter{}{}{}
\runningfooter{By Aaron G.K.}{}{Page \thepage\ of \numpages}
\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large Grade 11 Physics Homework 1\\
		$1^\text{st}$ Quarter}
	\maketitle
				\begin{questions}
					\question What are the most important ways in which physics has contributed to human society?
					\question What are the biggest challenges that physics faces in solving the problems of the 21st century?
					\question How can we make physics more accessible and engaging for people from all backgrounds?
					\question How can we use physics to create a more sustainable future for all?
					\question What are the most significant ways in which physics has improved the quality of human life?
					\question How can we design physics curricula and learning experiences that are more inclusive and equitable?
					\question What are the risks and benefits of new physics technologies, and how can we develop and use them responsibly?
					\question Discuss what you think are three of the best physics inventions/discoveries and why.
					
				\end{questions}	
			\end{document}