\documentclass[12pt,addpoints]{exam}
%\usepackage{enumitem}
\usepackage{amsfonts,amssymb,amsmath, amsthm}
\usepackage{graphicx}
\usepackage{systeme}
\usepackage{pgf,tikz,pgfplots}
\pgfplotsset{compat=1.15}
\usepgfplotslibrary{fillbetween}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=20mm,
	top=20mm,
}
\date{October, 2023}
\pagestyle{headandfoot}
%\firstpageheadrule
\runningheader{1st Quarter Midterm Examination}{}{Page \thepage\ of \numpages}
\runningheadrule
\firstpagefooter{}{}{}
\runningfooter{By Aaron G.K.}{}{Page \thepage\ of \numpages}
\begin{document}
	\title{St John Baptist De La Salle Catholic School, Addis Ababa\\
		\large Grade 11 Physics Midterm Examination \\
		$1^\text{st}$ Quarter}
	\maketitle
	\begin{center}
		\fbox{\fbox{\parbox{6in}{\centering
					Notes, and use of other aids is \textbf{NOT} allowed.  Read all directions carefully and \textbf{write your answers in the answer sheet}.  To receive full credit, you must show all of your work.
	}}}	\end{center}
	{Name:\underline{\hspace{2in}}\text{     }{Roll Number:\underline{\hspace{0.5in}}\text{     }{Section:\underline{\hspace{0.3in}}{Time Allowed: \bf{60  minutes}}
				\subsubsection*{Multiple Choice Questions}
				\begin{questions}
					\question When light travels from medium A to medium B, it refracts towards the normal. Which of the following is true?
					\begin{choices}
						\choice Light travels faster in medium B than medium A.
						\choice The wavelength of light in medium B is larger than its wavelength in medium A.
						\choice The frequency of light in medium B is larger than its frequency in medium A.
						\choice The refractive index of medium B is greater than that of medium A's.
					\end{choices}
					
					\subsubsection*{Workout Problems}
					\question Calculate the ratio of the highest to lowest frequencies of electromagnetic waves the eye can see, given the wavelength range of visible light is from 450 nm to 760 nm. Would we be able to observe and study human cells  which have an average diameter of about $100\mu m$? Why?\vspace{1.5in}
					\subsubsection*{Extra credit problems}
					\question A light ray entering an optical fiber surrounded by air is first refracted and then reflected as shown in the figure below. Show that if the fiber is made from crown glass($n=1.52$), any incident ray will be totally internally reflected.
				\end{questions}
				\subsection*{Answer Sheet}	
				\begin{tabular}{lllc}
					1.\noindent\rule{1.5cm}{0.4pt} & 6.\noindent\rule{1.5cm}{0.4pt}  & 11.\noindent\rule{1.5cm}{0.4pt}\vspace{0.5cm} \\ 
					2.\noindent\rule{1.5cm}{0.4pt} & 7.\noindent\rule{1.5cm}{0.4pt}  & 12.\noindent\rule{1.5cm}{0.4pt} \vspace{0.5cm} \\
					3.\noindent\rule{1.5cm}{0.4pt} & 8.\noindent\rule{1.5cm}{0.4pt} & 13.\noindent\rule{1.5cm}{0.4pt} \vspace{0.5cm}\\
					4.\noindent\rule{1.5cm}{0.4pt} & 9.\noindent\rule{1.5cm}{0.4pt} & 14.\noindent\rule{1.5cm}{0.4pt} \vspace{0.5cm}\\
					5.\noindent\rule{1.5cm}{0.4pt} & 10.\noindent\rule{1.5cm}{0.4pt} & 15.\noindent\rule{1.5cm}{0.4pt}\vspace{0.5cm}\\              
				\end{tabular}
			\end{document}